Sampling requirements to detect ecosystem change

### 2020-02-26 R/manuscript_draft.Rmd
changed the function to check the presence of package so it can be used for any future package. The function is called pkgTest()

```{r load_packages,echo=F,warning=F,message=F}
if (!require("pacman")){install.packages("pacman");library(pacman)}

>>>>

```{r load_packages,echo=F,warning=F,message=F}
pkgTest <- function(x)
{
  if (!require(x,character.only = TRUE))
  {
    install.packages(x,dep=TRUE)
    if(!require(x,character.only = TRUE)) stop("Package not found")
  }
  library(x, character.only = TRUE)
}

pkgTest("pacman")
